A Comprehensive Study of Characterizing Program Execution Time

### 2017-01-11 pt_characterization/data.old/paper2.tex
pt char paper

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
 \usepackage{auto-pst-pdf}
\usepackage{graphicx}
%\usepackage{arydshln}
\usepackage{ifpdf}
\ifpdf
  \usepackage{epstopdf}
\fi
\usepackage{multirow}
\usepackage{epsfig}
\usepackage{float}
\usepackage{url}
\usepackage{color}
\usepackage{subfigure}

@@

\paragraph{Dual 2048:} In Figure~\ref{fig:refined_dual_put2048}, ten points (outliers) are removed compared to that of Figure~\ref{fig:dual_put2048}.
\begin{figure}[h]
	\centering
	\subfigure[Refined Dual PUT2048]{%%%%  f
		\includegraphics[scale=0.4]{dual_put2048_new.eps}
		\label{fig:refined_dual_put2048}
	}
	\subfigure[The Focused Clump of Refined Dual PUT2048]{%%%% 
		\includegraphics[scale=0.4]{dual_put2048_new_trimmed.eps}
		\label{fig:fo_refined_dual_put2048_new_trimmed}
	}
	\caption{Refined Dual PUT2048 with {\tt rhn\_check} Removed.\label{fig:new_put2048}}
\end{figure}

%\begin{center}
%\line(1,0){480}
%\end{center}
\vspace{-.2in}

\paragraph{Dual 4096:} See Table~\ref{tab:exp_notes3} for the details of this run (on {\tt sodb8}). In Fig.~\ref{fig:refined_dual_put4096}, five points (outliers) are removed compared to that of Fig.~\ref{fig:dual_put4096}. 
{\color{blue}In particular, {\tt rhn\_check} with a significant time (771 msecs) is still included in one of the two outliers at the bottom right corner in Fig.~\ref{fig:refined_dual_put4096}.}
\begin{figure}[h]
	\centering
	\subfigure[Refined Dual PUT4096]{%%%%  five rows (57,250,331,394,456) removed
		\includegraphics[scale=0.4]{dual_put4096_new.eps}
		\label{fig:refined_dual_put4096}
	}
	\subfigure[The Focused Clump of Refined Dual PUT4096]{%%%% two more rows (123, 165) removed
		\includegraphics[scale=0.4]{dual_put4096_new_trimmed.eps}
		\label{fig:fo_refined_dual_put4096_new_trimmed}
	}
	\caption{Refined Dual PUT4096 with {\tt rhn\_check} Removed~\label{fig:new_put4096}}
\end{figure}

@@

\subsubsection{Influence of {\tt rhn\_check} on the Same Dual PUT}
Even though {\tt rhn\_check} is off, both halves' distributions look different. 
Dual PUT2048 reveals two bands above 1,026,300 msec in the second half (Fig.~\ref{fig:rc_off_new_dual2_put2048})
while exhibiting only three scattered points above 1,026,300 msec in the first half (Fig.~\ref{fig:first100_on_dual2_put2048}). 
In dual PUT4096, the second half (Fig.~\ref{fig:rc_off_new_dual2_put4096_v2}) also shows 
more variance than that of the first half (Fig.~\ref{fig:first100_on_dual2_put4096_v2}).

\begin{figure}[H]
	\centering
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual1_put2048_v2.eps}
		\label{fig:first100_on_dual1_put2048_v2}
	}
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual1_put2048_v2.eps}
		\label{fig:rc_off_new_dual1_put2048_v2}
	}
	\subfigure[2nd half's measured times on dual PUT2048 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual2_put2048.eps}
		\label{fig:first100_on_dual2_put2048}
	}
	\subfigure[2nd half's measured times on dual PUT2048 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual2_put2048.eps}
		\label{fig:rc_off_new_dual2_put2048}
	}
	\caption{Comparison of measured times on the same axes for dual PUT2048 in the presence/absence of {\tt rhn\_check}: some outliers excluded~\label{fig:rhn_check_effect1}}
\end{figure}

\begin{figure}[H]
	\centering
	\subfigure[1st half's measured times on dual PUT4096 with {\tt rhn\_check} on ]{
		\includegraphics[scale=0.4]{first_100_dual1_put4096.eps}
		\label{fig:first100_on_dual1_put4096}
	}
	\subfigure[1st half's measured times on dual PUT4096 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual1_put4096.eps}
		\label{fig:rc_off_new_dual1_put4096}
	}
	 \subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual2_put4096_v2.eps}
		\label{fig:first100_on_dual2_put4096_v2}
	}
	\subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual2_put4096_v2.eps}
		\label{fig:rc_off_new_dual2_put4096_v2}
	}
	\caption{Comparison of measured times on the same axes for dual PUT4096 in the presence/absence of {\tt rhn\_check}: some outliers excluded~\label{fig:rhn_check_effect2}}
\end{figure}

\begin{figure}[H]
	\centering
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual1_put2048.eps}
		\label{fig:first100_on_dual1_put2048}
	}
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual1_put2048.eps}
		\label{fig:rc_off_new_dual1_put2048}
	}
   \subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual2_put4096.eps}
		\label{fig:first100_on_dual2_put4096}
	}
	\subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual2_put4096.eps}
		\label{fig:rc_off_new_dual2_put4096}
	}
	\caption{Unrefined (full) measured times on dual PUT2048/PUT4096 in the presence/absence of {\tt rhn\_check}: Fig.~\ref{fig:first100_on_dual1_put2048} unrefined on Fig.~\ref{fig:first100_on_dual1_put2048_v2}, 
Fig.~\ref{fig:rc_off_new_dual1_put2048} on Fig.~\ref{fig:rc_off_new_dual1_put2048_v2}, 
Fig.~\ref{fig:first100_on_dual2_put4096} on Fig.~\ref{fig:first100_on_dual2_put4096_v2}, and  
Fig.~\ref{fig:rc_off_new_dual2_put4096} on Fig.~\ref{fig:rc_off_new_dual2_put4096_v2}, 	
	~\label{fig:rhn_check_effect3}}
\end{figure}

\subsection{Investigation about Periodic Appearance of Daemons in dual PUT experiments}
In this section we study a phenomenon of why some daemons ({\tt rhn\_check}, {\tt kslowd000}, and {\tt kslowd001}) 
appear to kick in the second half's execution of the dual PUT with a long task length.

\subsubsection{{\tt rhn\_check}}

\paragraph{Dual PUT2048:}
We examine the trace of regular PUT1024 by \underline{EMPv6}, to check when {\tt rhn\_check} kicks in.

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|l|l|l|l|} \hline
PUTx & Iter. \# & Proc. Name & Program Time (msec)\\ \hline
1024 & 13 & {\tt rhn\_check} & 534 \\ \hline
1024 & 27 & {\tt rhn\_check} & 18372 \\ \hline
1024 & 41 & {\tt rhn\_check} & 422 \\ \hline
1024 & 55 & {\tt rhn\_check} & 522 \\ \hline
1024 & 69 & {\tt rhn\_check} & 417 \\ \hline
1024 & 83 & {\tt rhn\_check} & 522 \\ \hline
1024 & 97 & {\tt rhn\_check} & 417 \\ \hline
1024 & 111 & {\tt rhn\_check} & 518 \\ \hline
1024 & 125 & {\tt rhn\_check} & 417 \\ \hline
1024 & 135 & {\tt rhn\_check} & 522 \\ \hline
1024 & 149 & {\tt rhn\_check} & 425 \\ \hline
1024 & 163 & {\tt rhn\_check} & 528 \\ \hline
1024 & 177 & {\tt rhn\_check} & 418 \\ \hline
1024 & 191 & {\tt rhn\_check} & 523 \\ \hline
1024 & 205 & {\tt rhn\_check} & 419 \\ \hline
1024 & 219 & {\tt rhn\_check} & 522 \\ \hline
1024 & 233 & {\tt rhn\_check} & 422 \\ \hline
1024 & 247 & {\tt rhn\_check} & 526 \\ \hline
1024 & 261 & {\tt rhn\_check} & 421 \\ \hline
\multicolumn{3}{|r|}{Total Appearances:} & 19 times\\ \hline
  \end{tabular}
  }
 \caption{{\tt rhn\_check} Appearance at Even Iterations of (Regular) PUT1024 with 300 measurements~\label{fig:rc_reg_put_1024_even}}
\end{table}

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|l|l|l|l|} \hline
PUTx & Iter. \# & Proc. Name & Program Time (msec)\\ \hline
1024 & 276 & {\tt rhn\_check} & 19748 \\ \hline
1024 & 290 & {\tt rhn\_check} & 382 \\ \hline
1024 & 298 & {\tt rhn\_check} & 537 \\ \hline
\multicolumn{3}{|r|}{Total Appearances:} & 3 times\\ \hline
  \end{tabular}
  }
 \caption{{\tt rhn\_check} Appearance at Odd Iterations of (Regular) PUT1024 with 300 measurements~\label{fig:rc_reg_put_1024_odd}}
\end{table}

\pagebreak
\paragraph{Dual PUT4096:}
We examine the trace of regular PUT2048 by \underline{EMPv6}, to check when {\tt rhn\_check} kicks in.

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|l|l|l|l|} \hline
PUTx & Iter. \# & Proc. Name & Program Time (msec)\\ \hline
2048 & 13 & rhn\_check & 378 \\ \hline
2048 & 27 & rhn\_check & 375 \\ \hline
2048 & 41 & rhn\_check & 374 \\ \hline
2048 & 55 & rhn\_check & 378 \\ \hline
2048 & 69 & rhn\_check & 383 \\ \hline
2048 & 89 & rhn\_check & 544 \\ \hline
2048 & 103 & rhn\_check & 542 \\ \hline
2048 & 117 & rhn\_check & 19810 \\ \hline
2048 & 131 & rhn\_check & 544 \\ \hline
2048 & 145 & rhn\_check & 540 \\ \hline
2048 & 159 & rhn\_check & 541 \\ \hline
2048 & 163 & rhn\_check & 374 \\ \hline
2048 & 177 & rhn\_check & 378 \\ \hline
2048 & 191 & rhn\_check & 373 \\ \hline
2048 & 205 & rhn\_check & 377 \\ \hline
2048 & 219 & rhn\_check & 376 \\ \hline
2048 & 233 & rhn\_check & 375 \\ \hline
2048 & 245 & rhn\_check & 378 \\ \hline
2048 & 259 & rhn\_check & 376 \\ \hline
2048 & 273 & rhn\_check & 374 \\ \hline
2048 & 287 & rhn\_check & 375 \\ \hline
\multicolumn{3}{|r|}{Total Appearances:} & 21 times\\ \hline
  \end{tabular}
  }
 \caption{{\tt rhn\_check}'s Appearance at Odd Iterations of (Regular) PUT2048 with 300 measurements~\label{fig:rc_reg_put_2048_odd}}
\end{table}

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|l|l|l|l|} \hline
PUTx & Iter. \# & Proc. Name & Program Time (msec)\\ \hline
2048 & 6 & {\tt rhn\_check} & 539 \\ \hline
2048 & 20 & {\tt rhn\_check} & 541 \\ \hline
2048 & 34 & {\tt rhn\_check} & 549 \\ \hline
2048 & 48 & {\tt rhn\_check} & 539 \\ \hline
2048 & 62 & {\tt rhn\_check} & 542 \\ \hline
2048 & 76 & {\tt rhn\_check} & 543 \\ \hline
2048 & 82 & {\tt rhn\_check} & 379 \\ \hline
2048 & 96 & {\tt rhn\_check} & 374 \\ \hline
2048 & 110 & {\tt rhn\_check} & 387 \\ \hline
2048 & 124 & {\tt rhn\_check} & 371 \\ \hline
2048 & 138 & {\tt rhn\_check} & 377 \\ \hline
2048 & 152 & {\tt rhn\_check} & 378 \\ \hline
2048 & 170 & {\tt rhn\_check} & 536 \\ \hline
2048 & 184 & {\tt rhn\_check} & 551 \\ \hline
2048 & 198 & {\tt rhn\_check} & 543 \\ \hline
2048 & 212 & {\tt rhn\_check} & 541 \\ \hline
2048 & 226 & {\tt rhn\_check} & 540 \\ \hline
2048 & 240 & {\tt rhn\_check} & 549 \\ \hline
2048 & 252 & {\tt rhn\_check} & 542 \\ \hline
2048 & 266 & {\tt rhn\_check} & 541 \\ \hline
2048 & 280 & {\tt rhn\_check} & 544 \\ \hline
2048 & 294 & {\tt rhn\_check} & 573 \\ \hline
\multicolumn{3}{|r|}{Total Appearances:} & 22 times\\ \hline
  \end{tabular}
  }
 \caption{{\tt rhn\_check}'s Appearance at Even Iterations of (Regular) PUT2048 with 300 measurements~\label{fig:rc_reg_put_2048_even}}
\end{table}

\subsubsection{{\tt kslowd000}}

\paragraph{Dual PUT2048:}
We examined the trace of regular PUT1024 by \underline{EMPv6} 
but had no record capturing {\tt kslowd000}.

\paragraph{Dual PUT4096:} 
We examined the trace of regular PUT2048 by \underline{EMPv6} 
but had no record capturing {\tt kslowd000}, either. 
But the daemon was found in 
every measurement of the dual PUT2048 data (Figs.~\ref{fig:rc_off_dual1_put2048} and~\ref{fig:rc_off_dual2_put2048}) by \underline{EMPv6} with {\tt rhn\_sd} ({\tt rhn\_check}) disabled.

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|l|l|l|l|} \hline
Dual PUTx & Iter. \# & Proc. Name & Program Time (msec)\\ \hline
2048 & 1 & {\tt kslowd000} & 103 \\ \hline
2048 & 3 & {\tt kslowd000} & 103 \\ \hline
2048 & 5 & {\tt kslowd000} & 103 \\ \hline
2048 & 7 & {\tt kslowd000} & 102 \\ \hline
2048 & 9 & {\tt kslowd000} & 102 \\ \hline
2048 & 11 & {\tt kslowd000} & 104 \\ \hline
2048 & 13 & {\tt kslowd000} & 103 \\ \hline
2048 & 15 & {\tt kslowd000} & 102 \\ \hline
2048 & 17 & {\tt kslowd000} & 103 \\ \hline
2048 & 19 & {\tt kslowd000} & 103 \\ \hline
2048 & 21 & {\tt kslowd000} & 103 \\ \hline
2048 & 23 & {\tt kslowd000} & 102 \\ \hline
2048 & 25 & {\tt kslowd000} & 103 \\ \hline
2048 & 27 & {\tt kslowd000} & 103 \\ \hline
2048 & 29 & {\tt kslowd000} & 102 \\ \hline
2048 & 31 & {\tt kslowd000} & 102 \\ \hline
2048 & 33 & {\tt kslowd000} & 103 \\ \hline
2048 & 35 & {\tt kslowd000} & 103 \\ \hline
2048 & 37 & {\tt kslowd000} & 102 \\ \hline
2048 & 39 & {\tt kslowd000} & 103 \\ \hline
2048 & 41 & {\tt kslowd000} & 103 \\ \hline
2048 & 43 & {\tt kslowd000} & 103 \\ \hline
2048 & 45 & {\tt kslowd000} & 103 \\ \hline
2048 & 47 & {\tt kslowd000} & 103 \\ \hline
2048 & 49 & {\tt kslowd000} & 104 \\ \hline
2048 & 51 & {\tt kslowd000} & 102 \\ \hline
2048 & 53 & {\tt kslowd000} & 102 \\ \hline
2048 & 55 & {\tt kslowd000} & 103 \\ \hline
2048 & 57 & {\tt kslowd000} & 103 \\ \hline
2048 & 59 & {\tt kslowd000} & 102 \\ \hline
2048 & 61 & {\tt kslowd000} & 103 \\ \hline
2048 & 63 & {\tt kslowd000} & 104 \\ \hline
2048 & 65 & {\tt kslowd000} & 103 \\ \hline
2048 & 67 & {\tt kslowd000} & 102 \\ \hline
2048 & 69 & {\tt kslowd000} & 104 \\ \hline
2048 & 71 & {\tt kslowd000} & 103 \\ \hline
2048 & 73 & {\tt kslowd000} & 102 \\ \hline
2048 & 75 & {\tt kslowd000} & 102 \\ \hline
2048 & 77 & {\tt kslowd000} & 103 \\ \hline
2048 & 79 & {\tt kslowd000} & 103 \\ \hline
2048 & 81 & {\tt kslowd000} & 102 \\ \hline
2048 & 83 & {\tt kslowd000} & 104 \\ \hline
2048 & 85 & {\tt kslowd000} & 103 \\ \hline
2048 & 87 & {\tt kslowd000} & 103 \\ \hline
2048 & 89 & {\tt kslowd000} & 103 \\ \hline
2048 & 91 & {\tt kslowd000} & 103 \\ \hline
2048 & 93 & {\tt kslowd000} & 103 \\ \hline
2048 & 95 & {\tt kslowd000} & 102 \\ \hline
2048 & 97 & {\tt kslowd000} & 102 \\ \hline
2048 & 99 & {\tt kslowd000} & 103 \\ \hline
\multicolumn{3}{|r|}{Total Appearances:} & 50 times\\ \hline
  \end{tabular}
  }
 \caption{{\tt kslowd000}'s Appearance at Odd Iterations of dual PUT2048 with 100 measurements~\label{fig:rc_dual_put_2048_odd}}
\end{table}

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|l|l|l|l|} \hline
Dual PUTx & Iter. \# & Proc. Name & Program Time (msec)\\ \hline
2048 & 2 & {\tt kslowd000} & 103 \\ \hline
2048 & 4 & {\tt kslowd000} & 102 \\ \hline
2048 & 6 & {\tt kslowd000} & 103 \\ \hline
2048 & 8 & {\tt kslowd000} & 103 \\ \hline
2048 & 10 & {\tt kslowd000} & 103 \\ \hline
2048 & 12 & {\tt kslowd000} & 102 \\ \hline
2048 & 14 & {\tt kslowd000} & 103 \\ \hline
2048 & 16 & {\tt kslowd000} & 103 \\ \hline
2048 & 18 & {\tt kslowd000} & 102 \\ \hline
2048 & 20 & {\tt kslowd000} & 102 \\ \hline
2048 & 22 & {\tt kslowd000} & 103 \\ \hline
2048 & 24 & {\tt kslowd000} & 103 \\ \hline
2048 & 26 & {\tt kslowd000} & 102 \\ \hline
2048 & 28 & {\tt kslowd000} & 103 \\ \hline
2048 & 30 & {\tt kslowd000} & 104 \\ \hline
2048 & 32 & {\tt kslowd000} & 104 \\ \hline
2048 & 34 & {\tt kslowd000} & 102 \\ \hline
2048 & 36 & {\tt kslowd000} & 103 \\ \hline
2048 & 38 & {\tt kslowd000} & 103 \\ \hline
2048 & 40 & {\tt kslowd000} & 103 \\ \hline
2048 & 42 & {\tt kslowd000} & 102 \\ \hline
2048 & 44 & {\tt kslowd000} & 103 \\ \hline
2048 & 46 & {\tt kslowd000} & 103 \\ \hline
2048 & 48 & {\tt kslowd000} & 102 \\ \hline
2048 & 50 & {\tt kslowd000} & 103 \\ \hline
2048 & 52 & {\tt kslowd000} & 103 \\ \hline
2048 & 54 & {\tt kslowd000} & 103 \\ \hline
2048 & 56 & {\tt kslowd000} & 103 \\ \hline
2048 & 58 & {\tt kslowd000} & 103 \\ \hline
2048 & 60 & {\tt kslowd000} & 103 \\ \hline
2048 & 62 & {\tt kslowd000} & 102 \\ \hline
2048 & 64 & {\tt kslowd000} & 102 \\ \hline
2048 & 66 & {\tt kslowd000} & 103 \\ \hline
2048 & 68 & {\tt kslowd000} & 103 \\ \hline
2048 & 70 & {\tt kslowd000} & 102 \\ \hline
2048 & 72 & {\tt kslowd000} & 103 \\ \hline
2048 & 74 & {\tt kslowd000} & 104 \\ \hline
2048 & 76 & {\tt kslowd000} & 103 \\ \hline
2048 & 78 & {\tt kslowd000} & 103 \\ \hline
2048 & 80 & {\tt kslowd000} & 103 \\ \hline
2048 & 82 & {\tt kslowd000} & 103 \\ \hline
2048 & 84 & {\tt kslowd000} & 102 \\ \hline
2048 & 86 & {\tt kslowd000} & 102 \\ \hline
2048 & 88 & {\tt kslowd000} & 103 \\ \hline
2048 & 90 & {\tt kslowd000} & 103 \\ \hline
2048 & 92 & {\tt kslowd000} & 102 \\ \hline
2048 & 94 & {\tt kslowd000} & 103 \\ \hline
2048 & 96 & {\tt kslowd000} & 103 \\ \hline
2048 & 98 & {\tt kslowd000} & 103 \\ \hline
2048 & 100 & {\tt kslowd000} & 102 \\ \hline
\multicolumn{3}{|r|}{Total Appearances:} & 50 times\\ \hline
  \end{tabular}
  }
 \caption{{\tt kslowd000}'s Appearance at Even Iterations of dual PUT2048 with 100 measurements~\label{fig:rc_dual_put_2048_even}}
\end{table}

\subsubsection{{\tt kslowd001}} 
We examined the trace of regular PUT2048 by \underline{EMPv6} 
but had no record capturing {\tt kslowd001}, either. 
But the daemon was found in 
every measurement of the dual PUT2048 data (Figs.~\ref{fig:rc_off_dual1_put2048} and~\ref{fig:rc_off_dual2_put2048}) by \underline{ EMPv6} with {\tt rhn\_sd} ({\tt rhn\_check}) disabled.

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|l|l|l|l|} \hline
Dual PUTx & Iter. \# & Proc. Name & Program Time (msec)\\ \hline
2048 & 1 & {\tt kslowd001} & 104 \\ \hline
2048 & 3 & {\tt kslowd001} & 103 \\ \hline
2048 & 5 & {\tt kslowd001} & 102 \\ \hline
2048 & 7 & {\tt kslowd001} & 103 \\ \hline
2048 & 9 & {\tt kslowd001} & 103 \\ \hline
2048 & 11 & {\tt kslowd001} & 102 \\ \hline
2048 & 13 & {\tt kslowd001} & 102 \\ \hline
2048 & 15 & {\tt kslowd001} & 103 \\ \hline
2048 & 17 & {\tt kslowd001} & 103 \\ \hline
2048 & 19 & {\tt kslowd001} & 102 \\ \hline
2048 & 21 & {\tt kslowd001} & 103 \\ \hline
2048 & 23 & {\tt kslowd001} & 103 \\ \hline
2048 & 25 & {\tt kslowd001} & 103 \\ \hline
2048 & 27 & {\tt kslowd001} & 102 \\ \hline
2048 & 29 & {\tt kslowd001} & 103 \\ \hline
2048 & 31 & {\tt kslowd001} & 103 \\ \hline
2048 & 33 & {\tt kslowd001} & 102 \\ \hline
2048 & 35 & {\tt kslowd001} & 102 \\ \hline
2048 & 37 & {\tt kslowd001} & 103 \\ \hline
2048 & 39 & {\tt kslowd001} & 103 \\ \hline
2048 & 41 & {\tt kslowd001} & 103 \\ \hline
2048 & 43 & {\tt kslowd001} & 103 \\ \hline
2048 & 45 & {\tt kslowd001} & 103 \\ \hline
2048 & 47 & {\tt kslowd001} & 102 \\ \hline
2048 & 49 & {\tt kslowd001} & 102 \\ \hline
2048 & 51 & {\tt kslowd001} & 103 \\ \hline
2048 & 53 & {\tt kslowd001} & 103 \\ \hline
2048 & 55 & {\tt kslowd001} & 102 \\ \hline
2048 & 57 & {\tt kslowd001} & 103 \\ \hline
2048 & 59 & {\tt kslowd001} & 104 \\ \hline
2048 & 61 & {\tt kslowd001} & 103 \\ \hline
2048 & 63 & {\tt kslowd001} & 102 \\ \hline
2048 & 65 & {\tt kslowd001} & 103 \\ \hline
2048 & 67 & {\tt kslowd001} & 103 \\ \hline
2048 & 69 & {\tt kslowd001} & 102 \\ \hline
2048 & 71 & {\tt kslowd001} & 102 \\ \hline
2048 & 73 & {\tt kslowd001} & 103 \\ \hline
2048 & 75 & {\tt kslowd001} & 103 \\ \hline
2048 & 77 & {\tt kslowd001} & 102 \\ \hline
2048 & 79 & {\tt kslowd001} & 104 \\ \hline
2048 & 81 & {\tt kslowd001} & 103 \\ \hline
2048 & 83 & {\tt kslowd001} & 103 \\ \hline
2048 & 85 & {\tt kslowd001} & 103 \\ \hline
2048 & 87 & {\tt kslowd001} & 103 \\ \hline
2048 & 89 & {\tt kslowd001} & 103 \\ \hline
2048 & 91 & {\tt kslowd001} & 102 \\ \hline
2048 & 93 & {\tt kslowd001} & 102 \\ \hline
2048 & 95 & {\tt kslowd001} & 103 \\ \hline
2048 & 97 & {\tt kslowd001} & 103 \\ \hline
2048 & 99 & {\tt kslowd001} & 102 \\ \hline
\multicolumn{3}{|r|}{Total Appearances:} & 50 times\\ \hline
  \end{tabular}
  }
 \caption{{\tt kslowd001}'s Appearance at Odd Iterations of dual PUT2048 with 100 measurements~\label{fig:rc_dual_put_2048_odd1}}
\end{table}

>>>>

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
 \usepackage{auto-pst-pdf}
\usepackage{graphicx}
%\usepackage{arydshln}
\usepackage{ifpdf}
\ifpdf
  \usepackage{epstopdf}
\fi
\usepackage{multirow}
\usepackage{epsfig}
\usepackage{float}
\usepackage{url}
\usepackage{subfigure}

@@

\paragraph{Dual 2048:} In Figure~\ref{fig:refined_dual_put2048}, ten points are removed compared to that of Figure~\ref{fig:dual_put2048}.

\begin{figure}[h]
	\centering
	\subfigure[Refined Dual PUT2048]{%%%%  f
		\includegraphics[scale=0.4]{dual_put2048_new.eps}
		\label{fig:refined_dual_put2048}
	}
	\subfigure[The Focused Clump of Refined Dual PUT2048]{%%%% 
		\includegraphics[scale=0.4]{dual_put2048_new_trimmed.eps}
		\label{fig:fo_refined_dual_put2048_new_trimmed}
	}
	\caption{Refined Dual PUT2048 with Significant {\tt rhn\_check} Removed~\label{fig:new_put2048}}
\end{figure}

\begin{center}
\line(1,0){480}
\end{center}

\paragraph{Dual 4096:} See Table~\ref{tab:exp_notes3} for the details of this run (on {\tt sodb8}). In Figure~\ref{fig:refined_dual_put4096}, 
five points are removed compared to that of Figure~\ref{fig:dual_put4096}.

\begin{figure}[h]
	\centering
	\subfigure[Refined Dual PUT4096]{%%%%  five rows (57,250,331,394,456) removed
		\includegraphics[scale=0.4]{dual_put4096_new.eps}
		\label{fig:refined_dual_put4096}
	}
	\subfigure[The Focused Clump of Refined Dual PUT4096]{%%%% two more rows (123, 165) removed
		\includegraphics[scale=0.4]{dual_put4096_new_trimmed.eps}
		\label{fig:fo_refined_dual_put4096_new_trimmed}
	}
	\caption{Refined Dual PUT4096 with Significant {\tt rhn\_check} Removed~\label{fig:new_put4096}}
\end{figure}

@@

\section{Influence of {\tt rhn\_check} on the Same Dual PUT}

\begin{figure}[H]
	\centering
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual1_put2048_v2.eps}
		\label{fig:first100_on_dual1_put2048_v2}
	}
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual1_put2048_v2.eps}
		\label{fig:rc_on_new_dual1_put2048_v2}
	}
	\subfigure[2nd half's measured times on dual PUT2048 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual2_put2048.eps}
		\label{fig:first100_on_dual2_put2048}
	}
	\subfigure[2nd half's measured times on dual PUT2048 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual2_put2048.eps}
		\label{fig:rc_on_new_dual2_put2048}
	}
	\caption{Comparison of measured times on the same axes for dual PUT2048 in the presence/absence of {\tt rhn\_check}: some outliers excluded)~\label{fig:rhn_check_effect1}}
\end{figure}

\begin{figure}[H]
	\centering
	\subfigure[1st half's measured times on dual PUT4096 with {\tt rhn\_check} on ]{
		\includegraphics[scale=0.4]{first_100_dual1_put4096.eps}
		\label{fig:first100_on_dual1_put4096}
	}
	\subfigure[1st half's measured times on dual PUT4096 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual1_put4096.eps}
		\label{fig:rc_on_new_dual1_put4096}
	}
	 \subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual2_put4096_v2.eps}
		\label{fig:first100_on_dual2_put4096_v2}
	}
	\subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual2_put4096_v2.eps}
		\label{fig:rc_on_new_dual2_put4096_v2}
	}
	\caption{Comparison of measured times on the same axes for dual PUT4096 in the presence/absence of {\tt rhn\_check}: some outliers excluded)~\label{fig:rhn_check_effect2}}
\end{figure}

\begin{figure}[H]
	\centering
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual1_put2048.eps}
		\label{fig:first100_on_dual1_put2048}
	}
	\subfigure[1st half's measured times on dual PUT2048 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual1_put2048.eps}
		\label{fig:rc_on_new_dual1_put2048}
	}
   \subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} on]{
		\includegraphics[scale=0.4]{first_100_dual2_put4096.eps}
		\label{fig:first100_on_dual2_put4096}
	}
	\subfigure[2nd half's measured times on dual PUT4096 with {\tt rhn\_check} off]{
		\includegraphics[scale=0.4]{new_dual2_put4096.eps}
		\label{fig:rc_on_new_dual2_put4096}
	}
	\caption{Complete measured times on dual PUT2048/PUT4096 in the presence/absence of {\tt rhn\_check}~\label{fig:rhn_check_effect3}}
\end{figure}
